---
title: "NFL"
author: ""
date: ""
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    fig_mobile: FALSE
---
<style>
.storyboard-nav .sbframelist {
  margin: 0 auto;
  width: 94%;
  height: 50px;
  overflow: hidden;
  text-shadow: none;
  margin-bottom: 8px;
}

.storyboard-nav .sbnext, .storyboard-nav .sbprev {
  float: left;
  width: 2%;
  height: 50px;
  font-size: 50px;
}
pre.sourceCode.r {
  background-color: #ffffff;
}
pre code {
  font-size: 12px;
}
body {
  padding-top: 60px;
  font-size: 12px;
}
.section.sidebar {
  top: 60px;
  background-color: rgba(0, 0, 0, 0.15);
}
.bg-primary {
  background-color: rgb(0, 0, 0, 0.7);
}
.storyboard-nav .sbframelist ul li.active {
  background-color: rgba(0, 0, 0, 0.7);
}
.nav-tabs-custom > .nav-tabs > li.active {
  border-top-color: rgba(0, 0, 0, 0.7);
}
.navbar-inverse {
  background-color: rgba(0, 0, 0, 1);
  border-color: rgba(0, 0, 0, 1);
}
</style>
```{r setup, include = FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(
  echo = FALSE,
  include = FALSE,
  # eval = FALSE,
  cache = TRUE,
  autodep = TRUE,
  # results = "markup",
  # fig.align = "center",
  # fig.show = "hide",
  fig.width = 8,
  fig.height = 8,
  # out.width = 6,
  # out.height = 6,
  # width = 80,
  warning = FALSE,
  message = FALSE
)
```

```{r vars_shiny}
evaluate_rs_only <- TRUE
yrs_rng <- 5
wks_rng <- 5

```

```{r packages}
library("dplyr")
library("stringr")
library("tidyr")
# library("readxl")
library("ggplot2")
```

```{r functions}

# This is for game results analysis.
ifelse_correct <-
  function(pred,
           actual,
           true = "correct",
           false = "incorrect") {
    ifelse(pred == actual, true, false)
  }
```

```{r vars_const}
wk_rs_last <- 17
gpwk <- 16
persons_dual <- c("Andrew", "Tony")
colors_dual <- c("darkorange", "dodgerblue")

path_data <- file.path("data", "db_nfl.xlsm")
readxl::excel_sheets(path_data)

```

```{r import}
# ws_persons <- "persons"
# persons_info <- path_data %>% readxl::read_excel(sheet = ws_persons)

ws_game_results <- "nfl_game_results"
suppressWarnings(
  game_results <- 
    path_data %>% 
    readxl::read_excel(sheet = ws_game_results)
)

# Change the n_max parameter because the first non-blank tm_pick_straight is not
# seen in the firs 1000 rows.
ws_game_picks <- "nfl_game_picks"

suppressWarnings(
  game_picks <- 
    path_data %>% 
    readxl::read_excel(sheet = ws_game_picks, guess_max = 2000)
)

cols_game_results <-
  setdiff(names(game_results), "game_results_name")
cols_game_picks <-
  c(
    # "id",
    "game_results_id",
    "person",
    "line_home_pick",
    # "tm_away_pts_pick",
    # "tm_home_pts_pick",
    "tm_pick_spread",
    "confidence_spread",
    "tm_pick_straight"
  )
game_picks_join <-
  game_results %>%
  select(one_of(cols_game_results)) %>% 
  left_join(game_picks %>% select(one_of(cols_game_picks)), by = c("id" = "game_results_id"))
```

```{r vars_const_calc}
rows_firstlast <-
  game_results %>%
  filter(!is.na(season) & !is.na(wk)) %>%
  # arrange(season, wk) %>%
  slice(c(1, n()))
first_results_row <- rows_firstlast %>%  slice(1)
last_results_row <- rows_firstlast %>% slice(n())

yr_first <- first_results_row %>% pull(season)
yr_curr <- last_results_row %>% pull(season)
wk_curr <- last_results_row %>% pull(wk)
if(wk_curr > wk_rs_last) {
  wk_curr <- wk_rs_last
}
if (yrs_rng > (yr_curr - yr_first)) {
  yrs_rng <- yr_curr - yr_first
}

wk_prev <- wk_curr - 1
yr_display_min <- yr_curr - yrs_rng
yr_display_max <- yr_curr
```

```{r viz_constants}
theme_custom <-
  teplot::theme_te(option = "a")

x_wk_vals <- seq(0, wk_rs_last, by = 1)
y_wk_vals <- seq(0, wk_rs_last, by = 2)
alpha_secondary <- 0.5
x_yr_vals <- seq(yr_display_min, yr_curr, by = 1)
```

```{r data_filt}
game_picks_join <-
  game_picks_join %>%
  filter(person %in% persons_dual) %>%
  # mutate(person = factor(person)) %>% 
  arrange(id, person)

if (evaluate_rs_only) {
  game_picks_join <-
    game_picks_join %>%
    filter(wk <= wk_rs_last)
}
```

```{r viz_line_picks_recent}
cols_dates <- c("season", "wk")
cols_game_id <- c(cols_dates, "tm_away", "tm_home")
cols_display_line_picks_recent <- c(cols_game_id, "person", "value")

# `distinct()` removes duplicate "Actual"s.
person_actual <- "Actual"
line_picks_recent <-
  game_picks_join %>%
  mutate(line_home = ifelse(is.na(line_home_open), line_home_close, line_home_open)) %>%
  select(-starts_with("line_home_[co]")) %>%
  tidyr::gather(line_type, value, line_home, line_home_pick) %>%
  mutate(person = ifelse(line_type == "line_home", person_actual, person) %>% 
           factor(levels = c(persons_dual, person_actual))) %>%
  select(one_of(cols_display_line_picks_recent)) %>%
  distinct()

# Debugging...
line_picks_recent %>% filter(person == "Actual") %>% tail()
line_picks_recent %>% filter(person == persons_dual[1]) %>% tail()

lab_title_line_picks_recent <- "\"Guessing the Lines\" Picks"
lab_subtitle_line_picks_recent <- sprintf("Week %.0f, %.0f", wk_curr, yr_curr)

persons_trips_1 <- c(persons_dual, person_actual)
color_default_1 <- "grey"
colors_trips_1_named <- stats::setNames(c(colors_dual, color_default_1), persons_trips_1)

width_dodge <- 0.5
viz_line_picks_recent <-
  line_picks_recent %>%
  filter(season == yr_curr, wk == wk_prev) %>%
  mutate(matchup = paste0(tm_away, "@", tm_home) %>% forcats::fct_reorder(value)) %>%
  ggplot(aes(x = value, y = matchup)) +
  ggstance::geom_pointrangeh(
    aes(xmin = 0, xmax = value, color = person),
    size = 1,
    position = ggstance::position_dodgev(width_dodge)
  ) +
  scale_color_manual(values = colors_trips_1_named) +
  theme_custom +
  labs(title = lab_title_line_picks_recent, subtitle = lab_subtitle_line_picks_recent) +
  labs(x = NULL, y = NULL)
viz_line_picks_recent
```

```{r line_picks_proc}
cols_display_line_picks <-
  c(cols_game_id, "person", "line_home", "line_home_pick")
line_picks_tidy <-
  game_picks_join %>%
  mutate(line_home = ifelse(is.na(line_home_open), line_home_close, line_home_open)) %>%
  select(-starts_with("line_home_[co]")) %>%
  select(one_of(cols_display_line_picks)) %>%
  mutate(person = factor(person, levels = c(persons_trips_1))) %>% 
  tidyr::spread(person, line_home_pick, fill = 0)
line_picks_tidy

person_tie <- "Tie"
compute_h2h_winner_abs_at <-
  function(data = NULL,
           col_x = persons_dual[1],
           col_y = persons_dual[2],
           col_ref = NULL,
           col_new = NULL,
           true_x = col_x,
           true_y = col_y,
           default = NA) {
    col_x_sym <- rlang::sym(col_x)
    col_y_sym <- rlang::sym(col_y)
    col_ref_sym <- rlang::sym(col_ref)
    col_new_sym <- rlang::sym(col_new)
    data %>%
      mutate(!!col_new_sym :=
               ifelse(
                 abs(!!col_x_sym - !!col_ref_sym) < abs(!!col_y_sym - !!col_ref_sym),
                 true_x,
                 ifelse(abs(!!col_x_sym - !!col_ref_sym) > abs(!!col_y_sym - !!col_ref_sym),
                        true_y,
                        default)
               ))
  }

line_picks_calc <-
  line_picks_tidy %>%
  compute_h2h_winner_abs_at(col_ref = "line_home", col_new = "winner", default = person_tie)
line_picks_calc

line_picks_summ_bywk <-
  line_picks_calc %>%
  group_by(season, wk, winner) %>%
  summarise(winner_cnt = n()) %>% 
  ungroup()

# line_picks_summ_bywk <-
#   line_picks_calc %>%
#   tidyr::gather(person, value, Andrew:Tony) %>% 
#   group_by(season, wk, person, winner) %>%
#   summarise(winner_cnt = n()) %>% 
#   ungroup()

# Debugging...
line_picks_summ_bywk %>% tail()

line_picks_bywk_spread <-
  line_picks_summ_bywk %>%
  group_by(season, winner) %>%
  tidyr::spread(winner, winner_cnt, fill = 0) %>%
  mutate_all(as.integer) %>% 
  ungroup() %>% 
  select(season, wk, !!!rlang::syms(persons_dual), !!rlang::sym(person_tie)) %>% 
  arrange(season, wk)
line_picks_bywk_spread %>% tail()
```

```{r viz_line_picks_bywk}
lab_title_line_picks_bywk <- "Head-to-Head \"Guessing the Lines\" Wins"
lab_subtitle_line_picks_bywk <- sprintf("By Week, %.0f", yr_curr)

persons_trips_2 <- c(persons_dual, person_tie)
color_default_2 <- color_default_1
colors_trips_2_named <- stats::setNames(c(colors_dual, color_default_2), persons_trips_2)

viz_line_picks_bywk <-
  line_picks_bywk_spread %>%
  tidyr::gather(person, cnt, -season, -wk) %>%
  mutate(person = factor(person, levels = persons_trips_2)) %>% 
  filter(season == yr_curr) %>%
  filter(wk < wk_curr) %>%
  ggplot(aes(x = wk, y = cnt)) +
  geom_pointrange(
    aes(ymin = 0, ymax = cnt, color = person), 
    size = 1,
    position = position_dodge(width_dodge)
  ) +
  scale_color_manual(values = colors_trips_2_named) +
  scale_x_continuous(breaks = x_wk_vals) +
  scale_y_continuous(breaks = y_wk_vals) +
  theme_custom +
  labs(title = lab_title_line_picks_bywk, subtitle = lab_subtitle_line_picks_bywk) +
  labs(x = NULL, y = NULL)
viz_line_picks_bywk
```

```{r line_picks_summ_byyr}
line_picks_bywk_spread_calc <-
  line_picks_bywk_spread %>%
  mutate(dummy = 0) %>% 
  compute_h2h_winner_abs_at(col_ref = "dummy", col_new = "winner", default = person_tie) %>% 
  select(-dummy) %>% 
  filter(!is.na(winner)) %>%
  filter(season != yr_curr | (season == yr_curr & wk < wk_curr))
line_picks_bywk_spread_calc %>% tail()

line_picks_summ_byyr <-
  line_picks_bywk_spread_calc %>%
  group_by(season, person = winner) %>%
  summarise(cnt = n()) %>% 
  ungroup()
line_picks_summ_byyr %>% tail()

line_picks_byyr_spread <-
  line_picks_summ_byyr %>%
  tidyr::spread(person, cnt) %>% 
  select(season, !!!rlang::syms(persons_dual), !!rlang::sym(person_tie)) %>% 
  arrange(season)
line_picks_byyr_spread %>% tail()
```

```{r viz_line_picks_byyr}
lab_title_line_picks_byyr <- "Head-to-Head \"Guessing the Lines\" Week Wins"
lab_subtitle_line_picks_byyr <- sprintf("By Season, %.0f - %.0f",  yr_display_min, yr_curr)
viz_line_picks_byyr <-
  line_picks_summ_byyr %>%
  mutate(person = factor(person, levels = persons_trips_2)) %>% 
  ggplot(aes(x = season, y = cnt)) +
  geom_pointrange(
    aes(ymin = 0, ymax = cnt, color = person), 
    size = 1,
    position = position_dodge(width_dodge)
  ) +
  scale_color_manual(values = colors_trips_2_named) +
  scale_y_continuous(breaks = y_wk_vals) +
  theme_custom +
  labs(title = lab_title_line_picks_byyr, subtitle = lab_subtitle_line_picks_byyr) +
  labs(x = NULL, y = NULL)
viz_line_picks_byyr
```

```{r results_picks_calc}
results_picks_calc <-
  game_picks_join %>%
  mutate(
    pick_result_spread = ifelse_correct(tm_pick_spread, tm_winner_spread),
    pick_result_straight = ifelse_correct(tm_pick_straight, tm_winner_straight)
  ) %>%
  filter(!is.na(pick_result_spread))
results_picks_calc

cols_display_results_picks_recent <-
  c(
    cols_game_id,
    "person",
    "line_home_pick",
    "tm_pick_spread",
    "confidence_spread",
    "pick_result_spread"
  )
results_picks_recent <-
  results_picks_calc %>%
  select(one_of(cols_display_results_picks_recent))
results_picks_recent %>% tail()
```

```{r results_picks_calc_recent}
lab_title_results_picks_recent <- "\"Guessing the Lines\" Picks"
lab_subtitle_results_picks_recent <- sprintf("Confidence, Week %.0f, .%.0f", wk_curr, yr_curr)

colors_dual_named <- stats::setNames(colors_dual, persons_dual)

viz_results_picks_recent <-
  results_picks_calc %>%
  filter(season == yr_curr, wk == wk_prev) %>%
  # mutate(matchup = paste0(tm_away, "@", tm_home) %>% forcats::fct_reorder(value)) %>%
  mutate(matchup = paste0(tm_away, "@", tm_home) %>% forcats::fct_reorder(confidence_spread)) %>% 
  ggplot(aes(y = matchup, x = confidence_spread)) +
  # scale_x_discrete(limits = c(0.1, 0.9)) +
  ggstance::geom_pointrangeh(
    aes(xmin = 0, xmax = confidence_spread, color = person), 
    size = 1, 
    position = ggstance::position_dodgev(width_dodge)
  ) +
  # scale_x_discrete(limits = c(0.5, 0.9)) +
  scale_color_manual(values = colors_dual_named) +
  theme_custom +
  labs(title = lab_title_results_picks_recent, subtitle = lab_subtitle_results_picks_recent) +
  labs(x = NULL, y = NULL)
viz_results_picks_recent

```
```{r viz_results_picks_recent}
arrow_padding <- 1.5
arrow_offset <- 5
w_home_t <- "Home Team Win"
w_home_f <- "Home Team Loss"
results_picks_calc_recent <-
  results_picks_calc %>%
  filter(season == yr_curr, wk == wk_prev) %>%
  mutate(matchup = paste0(tm_away, "@", tm_home)) %>%
  mutate(pts_h2a_diff = pts_home - pts_away) %>%
  mutate(w_home = if_else(pts_h2a_diff > 0, w_home_t, w_home_f)) %>%
  mutate(matchup = factor(matchup) %>% forcats::fct_reorder(line_home_close)) %>% 
  mutate(arrow_dir = ifelse(tm_pick_spread == tm_home, -1, 1)) %>%
  mutate(
    pick_arrow_end1 = line_home_close + arrow_padding * arrow_dir,
    pick_arrow_end2 = line_home_close + (arrow_padding + arrow_offset) * arrow_dir
  )

# colors_rg <- c("#00ba38", "#f8766d")
colors_rg <- c("red", "green")
w_home_tf <- c(w_home_t, w_home_f)
colors_rg_named <- stats::setNames(colors_rg, w_home_tf)
# scales::show_col(colors_rg)
point_size <- 12.5

colors_dual_and_rg_named <- stats::setNames(c(colors_dual, colors_rg), c(persons_dual, w_home_tf))

lab_title_results_picks_recent_2 <- lab_title_results_picks_recent
lab_subtitle_results_picks_recent_2 <- sprintf("Results, Week %.0f, .%.0f", wk_curr, yr_curr)

viz_results_picks_recent <-
  results_picks_calc_recent %>%
  ggplot() +
  geom_vline(aes(xintercept = 0), color = "black") +
  geom_segment(
    aes(
      y = matchup,
      x = pick_arrow_end1,
      yend = matchup,
      xend = pick_arrow_end2,
      color = person
    ),
    # position = ggstance::position_dodgev(0),
    size = 2,
    arrow = arrow(length = unit(0.1, "cm"))
  ) +
  # geom_point(
  #   data = results_picks_calc_recent,
  #   aes(y = matchup, x = line_home_close),
  #   shape = 21,
  #   # color = "black",
  #   size = point_size,
  #   inherit.aes = FALSE,
  # ) +
  geom_text(aes(y = matchup, x = line_home_close, label = line_home_close)) +
  geom_point(aes(y = matchup, x = pts_h2a_diff, color = w_home), size = point_size) +
  geom_text(aes(y = matchup, x = pts_h2a_diff, label = pts_h2a_diff)) +
  geom_segment(aes(
    y = matchup,
    x = line_home_close,
    yend = matchup,
    xend = pts_h2a_diff
  ),
  linetype = "dotted") +
  scale_color_manual(values = colors_dual_and_rg_named) +
  theme_custom +
  labs(title = lab_title_results_picks_recent_2, subtitle = lab_subtitle_results_picks_recent_2) +
  labs(x = NULL, y = NULL)
viz_results_picks_recent
```

```{r results_picks_bywk}
results_picks_summ <-
  results_picks_calc %>%
  group_by(season, wk, person, pick_result_spread) %>%
  summarise(cnt = n()) %>% 
  ungroup()
results_picks_summ %>% tail()

results_picks_bywk <-
  results_picks_summ %>%
  # tidyr::spread(pick_result_spread, cnt, sep = "_") %>%
  tidyr::spread(pick_result_spread, cnt) %>%
  mutate(correct_pct = correct / (correct + incorrect)) %>%
  ungroup() %>%
  group_by(season, person) %>%
  arrange(season, wk) %>% 
  mutate(correct_pct_td = cumsum(correct) / (cumsum(correct) + cumsum(incorrect))) %>% 
  ungroup()
results_picks_bywk %>% tail()
```

```{r viz_results_picks_bywk}
lab_title_results_picks_bywk <- "Accuracy of Game Picks, Against the Spread"
lab_subtitle_results_picks_bywk <- sprintf("By Week, %.0f", yr_curr)

viz_results_picks_bywk <-
  results_picks_bywk %>%
  filter(season == yr_curr) %>%
  ggplot(aes(x = wk, y = correct_pct)) +
  geom_pointrange(
    aes(
      ymin = 0,
      ymax = correct_pct,
      color = person
    ), 
    size = 1, 
    position = position_dodge(width_dodge)
  ) +
  geom_line(aes(x = wk, y = correct_pct_td, color = person), size = 1) +
  geom_hline(
    aes(yintercept = 0.5),
    color = "black",
    size = 1,
    linetype = "dashed"
  ) +
  scale_color_manual(values = colors_dual) +
  scale_x_continuous(breaks = x_wk_vals) +
  scale_y_continuous(labels = scales::percent_format(), limits = c(0, 1)) +
  theme_custom +
  labs(title = lab_title_results_picks_bywk, subtitle = lab_subtitle_results_picks_bywk) +
  labs(x = NULL, y = NULL)
viz_results_picks_bywk
```

```{r results_picks_byyr}
results_picks_byyr <-
  results_picks_bywk %>%
  group_by(season, person) %>%
  # mutate(correct_pct = correct / (correct + incorrect))
  summarise_at(vars(correct, incorrect), funs(sum), na.rm = TRUE) %>%
  mutate(correct_pct = correct / (correct + incorrect)) %>% 
  ungroup() %>% 
  group_by(person) %>%
  arrange(season) %>% 
  mutate(correct_pct_td = cumsum(correct) / (cumsum(correct) + cumsum(incorrect))) %>% 
  ungroup()
results_picks_byyr %>% tail()

```

```{r viz_results_picks_byyr}
lab_title_results_picks_byyr <- lab_title_results_picks_bywk
lab_subtitle_results_picks_byyr <- sprintf("By Year, %.0f - %.0f", yr_display_min, yr_curr)
viz_results_picks_byyr <-
  results_picks_byyr %>%
  ggplot(aes(x = season, y = correct_pct)) +
  geom_pointrange(
    aes(
      ymin = 0,
      ymax = correct_pct,
      color = person
    ), 
    size = 1, 
    position = position_dodge(width_dodge)
  ) +
  geom_line(aes(x = season, y = correct_pct_td, color = person), size = 1) +
  geom_hline(
    aes(yintercept = 0.5),
    color = "black",
    size = 1,
    linetype = "dashed"
  ) +
  scale_color_manual(values = colors_dual) +
  scale_x_continuous(breaks = x_yr_vals) +
  scale_y_continuous(labels = scales::percent_format(), limits = c(0, 1)) +
  theme_custom +
  labs(title = lab_title_results_picks_byyr, subtitle = lab_subtitle_results_picks_byyr) +
  labs(x = NULL, y = NULL)
viz_results_picks_byyr
```

```{r knit_cleanly}

knit_cleanly <- function(data = NULL) {
  data %>%
    mutate_if(is.numeric, funs(round(., 3))) %>% 
    knitr::kable(format = "html") %>% 
    kableExtra::kable_styling(full_width = F, position = "left")
}
```


Lines {.storyboard}
=

### This Week

```{r viz_line_picks_recent_show, include = TRUE, fig.show = "asis"}
viz_line_picks_recent
```

### This Week

```{r line_picks_recent_show, include = TRUE, results = "markup"}
line_picks_recent %>% 
  arrange(desc(season), desc(wk), person) %>%
  # head(wks_rng * gpwk * length(persons_dual)) %>% 
  filter(wk %in% c(wk_prev, wk_curr)) %>% 
  knit_cleanly()
```

### This Season

```{r viz_line_picks_bywk_show, include = TRUE, fig.show = "asis"}
viz_line_picks_bywk
```

### This Season

```{r line_picks_bywk_show, include = TRUE, results = "markup"}
line_picks_bywk_spread %>%
  arrange(desc(season), desc(wk)) %>% 
  # head(wks_rng) %>% 
  knit_cleanly()
```

### All Seasons

```{r viz_line_picks_byyr_show, include = TRUE, fig.show = "asis"}
viz_line_picks_byyr
```

### All Seasons

```{r line_picks_byyr_show, include = TRUE, results = "markup"}
line_picks_byyr_spread %>%
  arrange(desc(season)) %>% 
  # head(yrs_rng) %>% 
  knit_cleanly()
```

Results {.storyboard}
=

### This Week

```{r viz_results_picks_recent_show, include = TRUE, fig.show = "asis"}
viz_results_picks_recent
```

### This Week

```{r results_picks_recent_show, include = FALSE, results = "markup"}
results_picks_recent %>% 
  arrange(desc(season), desc(wk), person) %>%
  # head(wks_rng * gpwk * length(persons_dual)) %>% 
  filter(wk %in% c(wk_prev, wk_curr)) %>% 
  knit_cleanly()
```


### This Season

```{r results_picks_bywk_show, include = TRUE, results = "markup"}
results_picks_bywk %>%
  arrange(desc(season), desc(wk), person) %>%
  # head(wks_rng * length(persons_dual)) %>% 
  knit_cleanly()
```

### This Season

```{r viz_results_picks_bywk_show, include = TRUE, fig.show = "asis"}
viz_results_picks_bywk
```

### All Seasons

```{r viz_results_picks_byyr_show, include = TRUE, fig.show = "asis"}
viz_results_picks_byyr
```

### All Seasons

```{r results_picks_byyr_show, include = TRUE, results = "markup"}
results_picks_byyr %>%
  arrange(desc(season), person) %>%
  # head(yrs_rng * length(persons_dual)) %>% 
  knit_cleanly()
```

About
=

This about shows the "predictions" made by my brother (Andrew) and I (Tony)
for NFL games since 2012.
